---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
h2 {
  font-family: 'Tahoma';
  padding: 15px;
  color: #000000;
  text-align: center;
}

body {
  background-color: #edf4f2;
  color: #000000;
  font-size: 18px;
  text-align: center;
}

img {
  display: block;
  margin: 16px auto;
}
```

## What apps are people using when they open their phones?

This survey tracked observations of the first apps used when people open up their phones and the purpose behind why they opened their phones in the first place as well as the time spent on their phones while doing said activity.

```{r}
library(tidyverse)

options(scipen = 999)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTi8OcDqIiTnS37eRF-l1qUIuXkg6Dgaasf3GETIucqXC1jPpcGuyCWTtHwsWHP36DhJFdcigdWYDHM/pub?output=csv")
latest_data <- logged_data %>%
  rename(
    uses_phone = 2,
    purpose = 3,
    app = 4,
    time_spent = 5,
    enjoyment = 6,
  )

# Getting summary data
total_observations <- nrow(latest_data)
time_spent <- latest_data$time_spent
min_time <- min(time_spent)
max_time <- max(time_spent)
mean_time <- mean(time_spent)

enjoyment <- latest_data$enjoyment
min_enjoyment <- min(enjoyment)
max_enjoyment <- max(enjoyment)
mean_enjoyment <- mean(enjoyment)
```

Based on **`r total_observations`** observations of people using their phones the average time spent on each open of the phone was **`r format(round(mean_time), 1)`** minute(s) with the shortest time being **`r min_time`** minute(s) and the longest at **`r max_time`** minutes. The average enjoyment rating of the time spent on their phones was also recorded at **`r format(round(mean_enjoyment), 1)`** out of 5.



```{r}
# Finding the most common purpose and the count
purposes <- latest_data %>%
  count(purpose) %>%
  slice_max(n)

common_purpose <- purposes$purpose
common_purpose_count <- purposes$n
```

The graph below shows the variety of purposes or reasons behind why someone used their phone. The most common purpose logged was **`r common_purpose`** at a total of **`r common_purpose_count`**.

```{r}
# Graph of the purposes
ggplot(data = latest_data) + 
  geom_bar(
    aes(x = purpose, fill = purpose), show.legend = FALSE) +
  labs(
    title = "The purposes of opening the phone",
    x = "Purposes",
    y = "Count") +
  theme_classic()

# Finding the most common type of app used first
app <- latest_data %>%
  count(app) %>%
  slice_max(n)

common_app <- app$app
common_app_count <- app$n

```

The graph below shows the different types of apps people first went to when they opened their phones. The most common type of app logged was **`r common_app`** at a total of **`r common_app_count`** times.

```{r}
# Graph of the apps
ggplot(data = latest_data) + 
  geom_bar(
    aes(x = app, fill = app), show.legend = FALSE) +
  labs(
    title = "The apps used on first open",
    x = "Apps",
    y = "Count") +
  theme_classic()

```


